---
name: Amanda Danielle
surname: Perez
position: "Researcher and Instructor of Psychology"
profilepic: "./img/me.png"
www: amandaperez.netlify.app
email: "adp@berkeley.edu"
date: "`r format(Sys.time(), '%B %Y')`"
mobile: 
headcolor: 990000
docname: CV
output: 
  vitae::awesomecv:
    keep_tex: false
always_allow_html: yes
header-includes:
  \usepackage{multicol}
  \usepackage{colortbl}
  \arrayrulecolor{white}
  \usepackage{hhline}
  \definecolor{light-gray}{gray}{0.95}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)

packages <- c('vitae'     # The CV's LaTeX Template
             ,'tibble'    # Data sctructure for tribbles
             ,'magrittr'  # The Pipe %>%
             ,'here'      # Relative Filepaths
             ,'readr'     # Data Loading
            )
library(dplyr)
library(fontawesome)
# Install packages not yet installed
installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed_packages])
}

# Packages loading
lapply(packages, library, character.only = TRUE) %>%
  invisible()

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(ggplot2)
library(dplyr)
library(emojifont)
library(fontawesome)


source(file = here("r","data.r"))

```

# \faIcon{university} Education


```{r EDUCATION}

edu %>%
  detailed_entries(
    with = inst,
    what = degree,
    where = where, .protect = FALSE
  )

```



# \faIcon{lightbulb} Research Interests

```{r INTERESTS}

interests %>%
  detailed_entries(
    what = area, .protect = FALSE
       ) 

```


# \faIcon{chalkboard-teacher} Academic Appointments

```{r TEACHING}

teaching %>%
  detailed_entries(
    with = area,
    what = accomplishment,
  )

```

\newpage

# \faIcon{chalkboard} Assistant Teaching Experience

```{r ASSISTANT}

assistant %>%
  detailed_entries(
    with = area,
    what = accomplishment,
  )

```

# \faIcon{edit} Manuscripts Under Review or in prep

```{r PREP}

prep %>%
  detailed_entries(
    what = bib, .protect=FALSE
  )

```

# \faIcon{file} Publications

```{r PUBLISHED}

pub %>%
  detailed_entries(
    what = bib, .protect=FALSE
  )

```

\newpage

# \faIcon{medal} Distinctions

```{r HONORS}

honors %>%
  detailed_entries(
    what = accomplishment, .protect = FALSE
  )

```


# \faIcon{brain} Skills

```{r SKILLS}
tech %>%
  detailed_entries(
    what = accomplishment, .protect = FALSE
  )

skills %>%
  detailed_entries(
    with = area,
    what = skills
  )
workex %>%
  detailed_entries(
    what = accomplishment, .protect = FALSE
  )
workskills %>%
  detailed_entries(
    with = area,
    what = skills
  )
```

# \faIcon{comments} Conference Presentations

```{r CONFERENCE}
talks %>%
  detailed_entries(
    what = bib, .protect=FALSE
  )
```


# \faIcon{users} Mentoring & Advising

```{r, MENTOR}
mentor %>%
  detailed_entries(
    what = accomplishment, .protect = FALSE
  )
```

# \faIcon{black-tie} Professional Affiliations

```{r, MEMBER}
member %>%
  detailed_entries(
    what = accomplishment, .protect = FALSE
  )
```

# \faIcon{comment-alt} Invited Talks

```{r, TALKS}
invite %>%
  detailed_entries(
    what = accomplishment, .protect = FALSE
  )
```
 
\newpage
 
# \faIcon{school} Professional Development

```{r, PROFDEV}
profdev %>%
  detailed_entries(
    with = area,
    what = accomplishment, .protect = FALSE
  )
```



*CV made entirely in R using the vitae package*